Spectroscopic Characterization of New Er$^{3+}$ Host Crystals for Quantum Network Applications

### 2020-04-18 Draft.tex
Finish PLE; remove comments
Finish PL

\begin{itemize}
\item Why PLE? What can you measure, and what can you learn from those measurements?

\item How does our PLE setup work?

\item What limits our ability to measure smaller signals?
\end{itemize}

@@

@@

>>>>

@@

Emission spectroscopy is a different form of fluorescence spectroscopy, where instead of scanning the wavelength of the excitation laser, you measure the frequency composition of the fluorescence itself. In our experiment, this is done by focusing the fluorescence into a thin slit, which spatially separates the different wavelengths of light, and then imaging this spatial spectrum onto an array of photodetectors. Thus the readout of each bin of the array detector corresponds to the emission at a different wavelength of light.

The emission spectrum is different from the excitation spectrum, due primarily to the fact that higher energy states have lower occupation at lower temperatures. In principle, all of the same transitions are visible; however, while the $Z_{1}Y_{1}$ and $Z_{1}Y_{2}$ transitions might appear equally bright while performing excitation spectroscopy, the former might be substanitally brighter when performing emission spectroscopy if the thermal occupation of $Y_{1}$ is substantially higher than $Y_{2}$. Thus, the emission and excitation spectra might look very different, especially at low temperatures.

This is why it can be advantageous to measure both at the same time. By measuring the emission spectrum for a range of different excitation wavelengths, a so-called ``2D spectrum'' can be obtained. Especially in situations where \erbium is sitting at multiple different sites in the crystal and thus multiple spectra are accessible, this additional dimension of resolution can be helpful in distinguishing the different spectra.

@@

\begin{itemize}
\item What limits our ability to measure smaller signals with the commercial spectrometer? Why do we think Fourier transform spectroscopy could improve our ability to detect smaller signals?
